CONEM2024-0014 \\ AN EXACT METHOD FOR THE MULTI-PRODUCT P-BATCH PROCESSING TIME MAXIMIZATION PROBLEM

### 2024-05-30 accepted/CONEM2024/MBPTMP/Review/CONEM2024.tex
updating article - final version

This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}. The method applied consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems. The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX software, as well as platforms for the development of group work, such as GitHub and Google Classroom. The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.

>>>>

This work was developed following a practice-based learning approach, as described in the work of \cite{Fraga2022}. The method applied consists of identifying new optimization problems, and mathematically modeling as well as proposing new solution methodologies for the identified problems. The material used basically consists of information collected, such as information about the production process studied and information collected in scientific material, and technological tools, such as LINGO, CodeBlocks, Gummi, LaTeX, as well as platforms for the development of group work, such as GitHub and Google Classroom. The following sections present the new interger programming problem identified (MPpBPTM) and an exact analytical method developed for solving it.
